New lower bounds for Schur and weak Schur numbers

### 2021-04-07 article/article.tex
ajout tableau de données schur

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{computational theorem}{Computational Theorem}[theorem]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{remark}{Remark}[section]

@@

\begin{remark}
\(SE_+\) and \(S\) have the same asymptotic growth rate.
\end{remark}

\subsection{Inequaties on SE_+}

The main result on \(SE_+\) follows. It allows us to improve lower bounds on Schur numbers by computing \(SE_+\).

\begin{theorem}
Let \(n, k \in \mathbb{N}^*\), we have \\
\[ S(n+k) \geq SE_+(k+1)S(n) \]
\end{theorem}

Using a SAT solvers, we are able to exhibit adequate Schur partitions, i.e satisfying \(SE_+\) constraint, 
hence providing lower bound on \(SE_+\). We refer to such partition as \textit{templates}. Moreover, when using 
a template in the above formula, it is possible to get an additive constant. We seek templates providing "affine"
inequalities : \(aS(n+k) + b \) where \(a\) is a lower bound for \(SE_+(k+1)\). Further details can be found in the \hyperref[SAT]{SAT section}.
\subsection{}

@@

\begin{remark}
The performance of
\end{remark}

@@

\subsection{Weak Schur number five}
As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same type of methods as in the
 previous subsection.

\par
First

\begin{computational theorem}
If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). 
\end{computational theorem}

More precisely, we verified the following results using the glucose SAT solver [reference].

\begin{tabular}{| c | *{21}{ p{2mm} |}}
	\hline
	\(m_4\)                   &   4   &   5   &   6  &   7   &   8   &   9   &  10  &  11  &  12  &  13  &  14  &  15  &  16  &  17  &  18  &  19  &  20  &  21  &  22  &  23  &  24  \\ 
	\hline
	\(WS(4 | m_4) + 1\) &  55  &  59  &  60  &  59  &  59  &  60  &  60  &  60  &  60  &  64  &  63  &  64  &  61  &  64  &  63  &  65  &  65  &  65  &  65  &  66  &  67  \\
	\hline
	\(max~m_5\)           &        &       &        &        &       &        &       &        &        &       &        &       &        &       &        &        &       &        &       &        &  53  \\
	\hline
\end{tabular}

>>>>

\usepackage[table]{xcolor}

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{computational theorem}{Computational Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]

@@

\subsection{}

\subsection{New lower bounds for Schur numbers}

The previous inequalities gives new lower bounds for \(S(n)\) for
\( n \in [\![9,+\infty]\!] \backslash \{13\} \). We compute the lower
bounds values for \( n \in [\![8,15]\!] \) using the four different inequalities, please notice that the values for \( n = 8\) and \(n = 13\) were already obtained thanks to the first one, found by Rowley. The best lower bounds are highlighted.\\
\\
\begin{center}
\begin{tabular}{|*{5}{c|}}
    \hline
	 & 8 & 9 & 10 & 11 \\
	\hline
	\(33S(n-3) + 6 \) & \cellcolor{yellow} 5286 & 17694 & 55446 & 174444\\
	\hline
	\(111S(n-4) + 43 \) & 4927 & \cellcolor{yellow} 17803 & 59539 & 186523\\
	\hline
	\(380S(n-5) + 148 \) & 5088 & 16868 & \cellcolor{yellow} 60948 & \cellcolor{yellow} 203828 \\
	\hline
	\(1140S(n-6) + 528 \) & 5088 & 15348 & 50688 & 182928\\
	\hline
	\hline
	& 12 & 13 & 14 & 15 \\
	\hline
	\(33S(n-3) + 6 \) & 587505 & \cellcolor{yellow} 2011290 & 6726330 & 21072090\\
	\hline
	\(111S(n-4) + 43 \) & 586789 & 1976176 & 6765271 & 22624951 \\
	\hline
	\(380S(n-5) + 148 \) & \cellcolor{yellow} 638548 & 2008828 & \cellcolor{yellow} 6765288 & \cellcolor{yellow} 23160388 \\
	\hline
	\(1140S(n-6) + 528 \) & 611568 & 1915728 & 6026568 & 20295948 \\
	\hline
\end{tabular}
\end{center}

Except for 8, 9 and 13, the best lower bounds are obtained thanks to the third inequality \( 380S(n-5) + 148 \leqslant S(n) \). The table doesn't go any further, but the same inequality allows to improve the lower bounds for every \( n \in [\![15,+\infty]\!] \).

@@

@@

\subsection{Weak Schur number five}
As explained in the previous subsection, the search space used for showing that  \(WS(5) \geq 196\) may not contain optimal solution. In this subsection, 
we give necessary conditions for a hypothetical partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets using the same method as the previous subsection.
